Experiment 3: Calibration Analysis

### 2022-04-13 group-c/E3-analysis-calibration.Rmd
add calibration histogram, reknit manuscript

>>>>

#### Calibration Accuracy

```{r E3-cal Plot Calibration Accuracy, echo=FALSE}
ggplot(subject.calibration.score, aes(x=mean_percent_in_roi))+
  stat_bin(binwidth = 10)+
  labs(x="Calibration Accuracy\n(% of samples within 200px of calibration point)")+
  theme_minimal()+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title.y = element_blank())
```

#### Correlation with Effects
